Diagnoses and cell types

### 2025-10-16 analyses/infercnv-consensus-cell-type/exploratory-notebooks/reference-query-counts.Rmd
spell libraries

These librares are dominated by immune cell types with very few Unknown/tumor cells, but it's still worth running them through `inferCNV` while being aware that we _may_ experience issues with these samples.

>>>>

These libraries are dominated by immune cell types with very few Unknown/tumor cells, but it's still worth running them through `inferCNV` while being aware that we _may_ experience issues with these samples.
